\documentclass[mathserif]{beamer}%
%
\xdef\sharedPath{../shared}%
\RequirePackage{\sharedPath/latexStyles/slides}%
%
%
\title[Intro to \href{http://www.optimizationBenchmarking.org}{optimizationBenchmarking.org} Evaluator]{%
The \href{http://www.optimizationBenchmarking.org}{optimizationBenchmarking.org} Experiment Evaluation Framework}%
%
\author[Thomas Weise]{%
Thomas Weise\\%
\footnotesize{%
\href{mailto:tweise@ustc.edu.cn}{tweise@ustc.edu.cn} $\cdot$ %
\href{mailto:tweise@gmx.de}{tweise@gmx.de} $\cdot$ %
\href{http://www.it-weise.de}{http://www.it-weise.de}}}%
%
\institute[UBRI]{%
USTC-Birmingham Joint Res. Inst. in Intelligent Computation and Its Applications (UBRI)\\%
University of Science and Technology of China (USTC), Hefei 230027, Anhui, China%
}%
%
\date{\today}%
%
%
\begin{document}%
%
\startPresentation%
%
%
\section{Introduction}%
%
\begin{frame}[t]%
\frametitle{Optimization Algorithms}%
\begin{itemize}%
\item Many questions in the real world are actually optimization problems\only<2->{, e.g.,
\begin{itemize}%
%
\item \only<-6>{Find the \emph{shortest} tour for a salesman to visit Beijing, Chengdu, Shanghai, Wuhan, Xianggang, and return to Hefei!}\only<7->{\alert<7>{Traveling Salesman Problem}\scitep{ABCC2006TTSPACS,LLKS1985TTSPAGTOCO,GP2004TTSPAIV,L2011SGEFTSPIMSS}}%
%
\item<3-> \only<-6>{I need to transport $n$ items from here to Feixi but they are too big to transport them all at once. How can I load them best into my car so that I have to travel back and forth the least times?}\only<7->{\alert<7>{Bin Packing Problem}\scitep{KSH1995EHFTBPP}}%
%
\item<4-> \only<-6>{Which setting of $x_1$, $x_2$, $x_3$, and $x_4$ can make $(x_1\lor\lnot x_2 \lor x_3)\land(\lnot x_2\lor\lnot x_3 \lor x_4) \land (\lnot x_1\lor\lnot x_3 \lor \lnot x_4)$ become true (or, at least, as \emph{many} of its terms as possible)?}\only<7->{\alert<7>{Maximum (3-)Satisfiability Problem}\scitep{HS2000SAORFROS,TH2004UAIAEEFSAFSAMS,S1978TCOSP,RMK2000EASP}}%
%
\item<5-> \only<-6>{I want to build a large factory with $n$ workshops. I know the flow of material between each two workshops and now need to choose the locations of the workshops such that the overall running cost incurred by material transportation is \emph{minimized}.}\only<7->{\alert<7>{Quadratic Assignment Problem}\scitep{MF1999ACOMATSAACFTQAP,GTD1999ACOQAP}}%
\end{itemize}%
}%
%
\item<6-> Many optimization problems are \alert<7>{$\mathcal{NP}$-hard}, meaning that finding the best possible solution will usually not be possible in feasible time.%
%
\item<8-> We use metaheuristic optimization algorithms to give us good approximate solutions within acceptable runtime.%
%
\item<9-> Examples of such algorithms are\only<-19>{ %
Evolutionary Algorithms\scitep{BFM1997EA,CWM2011VOEAFRWA,BFM2000EC1BAAO,BFM2000EC2BAAO,DLJD2000EC,EM1999EC,CDGDMPP1999NIIO,GT2002AIECTAA,WGOEB}\uncover<10->{, %
Ant Colony Optimization\scitep{DMC1996ACO,DS2004ACO,GM2002APBATDOP,ZBMD2004MBSFCOACS,WGOEB}\uncover<11->{, %
Evolution Strategies\scitep{R1965ES,R1973ES,R1994ES,S1965KYASDEFIDS,S1968EOEZDT1,S1975EUNO,WGOEB}\uncover<12->{, %
Differential Evolution\scitep{WGOEB}\uncover<13->{, %
Particle Swarm Optimization\scitep{WGOEB}\uncover<14->{, %
Estimation of Distribution Algorithms\scitep{PSL2005DE,F2006DE,MMVRCC2006DE,BZSM2006DE,LZ2000DE,MM2005DE,BVPK2006DE,S2010DEFCFOAABKPARS}\uncover<15->{, %
CMA-ES\scitep{HOG1995ESAD,HO1996AANMDIESTCMA,HO2001ESCMA,HMK2003RTTCOTDESWCMACE,HK2004ETCESOMTF,H2006TCESACR,AH2005ARCESWIPS,AH2005PEOAALSEA}\uncover<16->{, and %
Local Search methods\scitep{HS2005SLSFAA,AL1997LSICO,DBSD2001DOILSA}\uncover<17->{ such as %
Simulated Annealing\scitep{SSF2002FCAIFSA,LA1987SATAA,B1987GAASA,JCS2003HC,KGV1983SA,VC1985SA,DPSW1982MCTICO,DPSW1982MCTICO2,P1970AMCMFTASOCTOCOP,WGOEB}\uncover<18->{ or %
Tabu Search\scitep{G1989TSPI,G1990TSPII,GL1993TABU,DWH1989TSTATAAATNN,BT1994TABU}\uncover<19->{, %
as well as hybrids of local and global search, such as Memetic Algorithms\scitep{M1989MA,M2002MA,MC2003AGITMA,ES2003HWOTMA,HKS2005RAIMA,DM2004MA,RS1994FMA}%
}}}}}}}}}}}\only<20->{\dots\ many}%
%
\item<20-> \alert<20>{Which of them is best (for my problem)?}%
\item<21-> \alert<21>{How can I make a good algorithm better (for my problem)?}%
%
\end{itemize}%
\end{frame}%
%
\begin{frame}[t]%
\frametitle{Algorithm Analysis and Comparison}%
\begin{itemize}%
\item Traditional Approach {\`{a}} la \emph{``QuickSort is better than Bubble Sort because it needs $\mathcal{O}(n \log n)$ while Bubble Sort needs $\mathcal{O}(n^2)$ steps in the average case.''}%
%
\item<2-> Complexity Analysis, Theoretical Bounds of Runtime and Solution Quality%
\item<3-> \alert<-9>{Usually not feasible}\uncover<4->{%
\begin{itemize}%
\item analysis extremely complicated\uncover<5->{ since%
\item<5-> algorithms are usually randomized\uncover<6->{ and%
\item<6-> have many parameters (e.g., crossover rate, population size)\uncover<7->{ and%
\item<7-> ``sub-algorithms'' (e.g., crossover operator, mutation operator, selection algorithm)%
\item<8-> optimization problems also differ in many aspects%
\item<9-> Theoretical results only available for toy problems and extremely simplified algorithms.%
\item<10-> \alert<10>{Currently, not mature enough to be an easy-to-use tool for practitioners}%
}}}%
\end{itemize}%
}%
%
\item<11-> Experimental analysis and comparison only practical alternative.%
%
\end{itemize}%
\end{frame}%
%
%
%
\begin{frame}%
\frametitle{Performance and Anytime Algorithms}%
%
\emph{``We use metaheuristic optimization algorithms to give us \alert<3->{good approximate solutions} within \alert<4->{acceptable runtime}.''}%
%
\uncover<2->{%
\begin{itemize}%
\item Algorithm performance has two dimensions\scitep{NAFR2010RPBBOB2ES,WCTLTCMY2014BOAAOSFFTTSP}:\uncover<3->{ solution quality\uncover<4->{ and required runtime}}.%
\item<5-> Anytime Algorithms\scitep{BD1989STDPP2} are optimization methods which have a guess about what the optimum could be at \emph{any time} during their run and which iteratively improve this guess.%
\item<6-> All metaheuristics are Anytime Algorithms.%
\item<7-> Several exact methods like Branch-and-Bound\scitep{LMSK1963AAFTTSP,Z1993TBABACSOTATSP,Z1999TAADFBABACSOTATSP} are Anytime Algorithms.%
\item<8-> Consequence: Most optimization algorithms produce approximate solutions of different qualities at different points during their process.%
\item<9-> Experiments must capture solution quality and runtime data.%
\end{itemize}%
}%
\end{frame}%
%
\AtBeginSection[]{%
\begin{frame}%
\frametitle{Section Outline}%
\tableofcontents[currentsection]%
\end{frame}%
}%
%
\section{The Framework}%
%
\begin{frame}%
\frametitle{Structure of the Framework}%
\end{frame}%
%
\endPresentation%
%
\end{document}%
%
\endinput%
